\documentclass{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{framed}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{enumerate}
\usepackage{graphicx} % Allows including image
\usepackage{hyperref}
\hypersetup{
  linkcolor  = blue,
  citecolor  = blue,
  urlcolor   = blue,
  colorlinks = true,
} % color setup
\usepackage[utf8]{inputenc}
\usepackage[top=1 in,bottom=1in, left=0.5 in, right=1 in]{geometry}
\usepackage{float} % for "H" placement specifier
\usepackage[authoryear]{natbib}
\usepackage{indentfirst}
\usepackage[dvipsnames]{xcolor}
\usepackage{float}
\usepackage{array}

\DeclareUnicodeCharacter{FB01}{fi}
\DeclareUnicodeCharacter{FF0C}{,}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\setlength\extrarowheight{1pt}

\newcommand\red[1]{{\color{red}#1}}

\bibliographystyle{plainnat}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\title{Supplementary Files for Comparing baseball players across eras via the novel Full House Model}

\author{Shen Yan$^1$, Adrian Burgos Jr.$^2$, Christopher Kinson$^1$, Brandon Niedert$^3$, \\and Daniel J. Eck$^1$}
\date{}

\begin{document}
\maketitle

{\centering
1. Department of Statistics, University of Illinois Urbana-Champaign \\
2. Department of History, University of Illinois Urbana-Champaign \\
3. FuboTV Inc. \\}

\vspace*{0.25cm}

\section{Data Collection for Batting Statistics}

Baseball-Reference Win Above Replacement(bWAR) is collected from the website: \url{https://www.baseball-reference.com/data/war_daily_bat.txt}, which is stored in batters\_bWAR.csv. 

\bigskip

Fangraphs Win Above Replacement(fWAR) is scraped from the website: \url {https://www.fangraphs.com/leaders.aspx?pos=all&stats=bat&lg=al&qual=0&type=c,4,5,6,23,58&season=2021&month=0&season1=2021&ind=0&team=0&rost=&age=&filter=&players=&startdate=&enddate=}, which is stored in batters\_fWAR.csv

\bigskip

Hits, Home Runs, and Walks are collected from Chadwick Baseball Bureau \url{http://www.chadwick-bureau.com/} and they provide data to a number of high-profile clients across the industry, including being a primary provider of historical statistical data for Baseball-Reference for major, minor, international, collegiate, and summer collegiate competitions. The datasets we use are listed on Github: \url{https://github.com/chadwickbureau/baseballdatabank/tree/master/core} and stored in the raw\_batter.csv.

%\textbf{These are not collected from GitHub, they are collected from an organization that collects these statistics. You need to name that organization.}


\bigskip

Hits, Runs, and Home Runs in a team's home and road games are collected from Chadwick Baseball Bureau \url{http://www.chadwick-bureau.com/} that is mentioned above. The datasets we use are listed on Github: \url{https://github.com/chadwickbureau/retrosplits/tree/master/daybyday} and stored in the team-xx.csv. 
%\textbf{These are not collected from GitHub, they are collected from an organization that collects these statistics. You need to name that organization.}

\bigskip

The unique player IDs for Baseball-Reference, and Fangraphs are collected from Chadwick Baseball Bureau \url{http://www.chadwick-bureau.com/} that is mentioned above. The unique player IDs for Baseball-Reference, and Chadwick are also collected from Chadwick Baseball Bureau \url{http://www.chadwick-bureau.com/}. The datasets we use are stored in people\_bb\_f.csv and people\_park\_bb.csv. 

 \section{Data Preprocess for Batting Statistics}

merge\_pop.R combines the bWAR, fWAR, and other statistics when a player is traded in midseason. Also, it adds the corresponding MLB eligible population to the dataset. The results are stored in the batters\_combined\_b.csv and batters\_combined\_f.csv

\bigskip

park\_factor\_chad.R applies the park-factor adjustment to the Hits, Runs, and Home Runs. Also, it combines the Hits, Home Runs, and other statistics when a player is traded in midseason and adds the corresponding MLB eligible population to the dataset. The results are stored in the batter\_park\_factor.csv. 

\bigskip

clean\_batters.R combines all the important batting statistics based on the players' unique IDs in Baseball-Reference, Fangraphs, and Chadwick. The results are stored in the batters\_all.csv. 

\section{Data Collection for Pitching Statistics}

Baseball-Reference Win Above Replacement(bWAR) is collected from the website: \url{https://www.baseball-reference.com/data/war_daily_pitch.txt}, which is stored in pitchers\_bWAR.csv. 

\bigskip

Fangraphs Win Above Replacement(fWAR) is scraped from the website: \url {https://www.fangraphs.com/leaders.aspx?pos=all&stats=pit&lg=al&qual=y&type=8&season=2021&month=0&season1=2021&ind=0&team=0&rost=0&age=0&filter=&players=0&startdate=&enddate=}, which is stored in pitchers\_fWAR.csv

\bigskip

Earned Run Average(ERA), Strikeouts(SO), and other statistics are collected from Chadwick Baseball Bureau \url{http://www.chadwick-bureau.com/} that is mentioned above. The datasets we use are listed on Github: \url{https://github.com/chadwickbureau/baseballdatabank/tree/master/core} and stored in Pitching.csv.

\section{Data Preprocess for Pitching Statistics}


merge\_pop\_p.R combines the bWAR, fWAR, and other statistics when a player is traded in midseason. Also, it adds the corresponding MLB eligible population to the dataset. The results are stored in the pitchers\_combined\_b.csv and pitchers\_combined\_f.csv

\bigskip

clean\_batters.R applies the park-factor adjustment to the Runs. Also, it combines all the important pitching statistics based on the players' unique IDs in Baseball-Reference, Fangraphs, and Chadwick. The results are stored in the pitchers\_all.csv. 

\section{Summary}

All the datasets and codes mentioned above can be found on Github: \url{https://github.com/yanshenlmx/Full_House_model_data} and our data processing steps are reproducible in Tech\_Report.html that is included with this submission.

%\vspace*{1cm}\textbf{Add a Section that states that our data processing steps are reproducible in NAME OF DOCUMENT that is included with this submission}


\end{document}